Learning Auditory Similarities Between Instrumental Playing Techniques

### 2020-04-04 paper/paper.tex
bis

The previous section described our methods for extracting spectrotemporal modulations in audio signals, as well as learning a non-Euclidean similarity metric between them.
We now turn to apply these methods to the problem of browsing a large-scale digital library of isolated musical notes, involving an extended vocabulary of playing techniques.
% TODO VL: organize design choices.
% (1) temporal support
% (2) time-frequency scattering / time scattering
% (3) learning / no learning

>>>>

The previous section described our methods for extracting spectrotemporal modulations in audio signals, as well as learning a non-Euclidean similarity metric between them.
We now turn to apply these methods to the problem of allocating isolated musical notes to clusters of a timbre similarity graph $\mathcal{G}_0$.
In practice, for training and evaluation purposes, the graph $\mathcal{G}_0$ stems from the consensus of $K=31$ users of the Cyberlioz web application, which was described in the \ref{sec:survey} section.
% browsing a large-scale digital library of isolated musical notes, involving an extended vocabulary of playing techniques.

% TODO VL: organize design choices.
% (1) temporal support
% (2) time-frequency scattering / time scattering
% (3) learning / no learning
